WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-12-22 summary/sec_2-research_limitations.tex
Add not explicitly testing for high-availability as a limitation

>>>>

\emph{Explicitly not testing for high availability}:
\gkc{By default, the container orchestration framework is handling service failures, auto scaling, auto down scaling, and independent service deployments. Also, when considering about modern cloud resources in data centers have better availability as well and failure handling. Combining both of factors will enable high availability for the \acrshort{wdias} system. But in this research, we are not heavily rely on those third party tools. Also, we do not explicitly test for the high availability with performing manually terminating services, and letting crash some of the services to measure how is it affect on the \acrshort{wdias} system high availability.}
